Supplementary Methods for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-11-30 Documents/supplementary_information.tex
Stop trying to hyperlink to external document.

We developed a mathematical model of HIV transmission and progression
that stratifies HIV infection into acute, chronic undiagnosed, chronic
diagnosed, chronic treated, chronic virally suppressed, and AIDS,
along with uninfected unvaccinated and vaccinated people
(\autoref{model} \&
\hyperref[model_diag]{Extended Data Fig.~\ref*{model_diag}}), tailored
to each of 127 countries.  Simulations of our model project the number
of people in each HIV stratum from 2015 to 2035, from which statistics
such as prevalence and incidence were calculated.  To evaluate the
impact of the 90--90--90 and 95--95--95 UNAIDS goals, model transition
rates were adjusted dynamically to meet intervention goals for
diagnosis, treatment, viral suppression, and vaccination coverage
(\autoref{targets}).  Data and estimates from many sources, including
The World Bank and UNAIDS, were used to parametrize the model
(\autoref{data_sources}).  Country-specific transmission rates were
fitted to estimates of the historical trajectories of incidence and
prevalence, spanning from as early as 1990 for some countries
(\autoref{model_fitting}). For every scenario of intervention
combinations, we conducted 1000 model simulations, sampling values of
model parameters from empirical distributions for each simulation, and
reported the results with median and percentiles
(\autoref{uncertainty}).

>>>>

We developed a mathematical model of HIV transmission and progression
that stratifies HIV infection into acute, chronic undiagnosed, chronic
diagnosed, chronic treated, chronic virally suppressed, and AIDS,
along with uninfected unvaccinated and vaccinated people
(\autoref{model} \& Extended Data Fig.~\ref*{model_diag}), tailored to
each of 127 countries.  Simulations of our model project the number of
people in each HIV stratum from 2015 to 2035, from which statistics
such as prevalence and incidence were calculated.  To evaluate the
impact of the 90--90--90 and 95--95--95 UNAIDS goals, model transition
rates were adjusted dynamically to meet intervention goals for
diagnosis, treatment, viral suppression, and vaccination coverage
(\autoref{targets}).  Data and estimates from many sources, including
The World Bank and UNAIDS, were used to parametrize the model
(\autoref{data_sources}).  Country-specific transmission rates were
fitted to estimates of the historical trajectories of incidence and
prevalence, spanning from as early as 1990 for some countries
(\autoref{model_fitting}). For every scenario of intervention
combinations, we conducted 1000 model simulations, sampling values of
model parameters from empirical distributions for each simulation, and
reported the results with median and percentiles
(\autoref{uncertainty}).
